---
title: "CaseStudy_Imperviousness"
author: "Yomna Eid"
date: "2026-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Check for the correct working directory, and make sure that the data is locally present in the ./Data folder within your directory. The dataset is the High Resolution Layer maps for Impervioussness Density provided by the Copernicus Monitoring Service, with a native resolution of 20m for the years 2006, 2009, 2012, 2015, and 2018.

```{r}
getwd()

maps <- list.files(path = "./Data/Imperviousness", pattern = "\\.tif$", recursive = TRUE,  full.names = TRUE)
```

Load the packages:

```{r}
library(stars)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dplyr)
```

Define the Na-value, and subset the dataset to our AOI (which is the state of North-Rhine Westphalia in Germany)

```{r}
nodata_value <- 250
imperviousness <- lapply(maps, function(file) {
  read_stars(file, NA_value = nodata_value)
})
attr(imperviousness, "NA_value") <- nodata_value

NRW <- ne_states(country = "germany") %>% filter(name == "Nordrhein-Westfalen") |> st_transform(st_crs(imperviousness[[1]]))

threshold_value <- 30
```

Using a threshold value of 30% imperviousness, for each year that the map is provided (2006 to 2018), the subsetted dataset is classified into a binary non-impervious (or 0 if less than 30%) and impervious (or 1 if more than 30%)

For the 3-year period of 2005, 2006, 2007

```{r}
imperv_2006 <- do.call(st_mosaic, imperviousness[1:2]) %>% st_crop(NRW$geometry) %>% st_apply(c("x", "y"), function(x) {
  ifelse(x > threshold_value, 1, 0)}) %>% setNames("imperviousness_2006")
attr(imperv_2006, "year") <- 2006

plot(imperv_2006)
```

For the 3-year period of 2008, 2009, 2010

```{r}
imperv_2009 <- do.call(st_mosaic, imperviousness[3:4]) %>% st_crop(NRW$geometry) %>% st_apply(c("x", "y"), function(x) {
  ifelse(x > threshold_value, 1, 0)}) %>% setNames("imperviousness_2009")
attr(imperv_2009, "year") <- 2009

plot(imperv_2009)
```

For the 3-year period of 2011, 2012, 2013

```{r}
imperv_2012 <- do.call(st_mosaic, imperviousness[5:6]) %>% st_crop(NRW$geometry) %>% st_apply(c("x", "y"), function(x) {
  ifelse(x > threshold_value, 1, 0)}) %>% setNames("imperviousness_2012") 
attr(imperv_2012, "year") <- 2012

plot(imperv_2012)
```

For the 3-year period of 2014, 2015, 2016

```{r}
imperv_2015 <- do.call(st_mosaic, imperviousness[7:8]) %>% st_crop(NRW$geometry) %>% st_apply(c("x", "y"), function(x) {
  ifelse(x > threshold_value, 1, 0)}) %>% setNames("imperviousness_2015")
attr(imperv_2015, "year") <- 2015

plot(imperv_2015)
```

For the 3-year period of 2017, 2018, 2019

```{r}
## Native resolution is 10m
imperv_2018 <- do.call(st_mosaic, imperviousness[9:65]) %>% st_crop(NRW$geometry) %>% st_apply(c("x", "y"), function(x) {
    ifelse(x > threshold_value, 1, 0)}) %>% setNames("imperviousness_2018") #%>%  st_downsample(c(1,1))
attr(imperv_2018, "year") <- 2018

plot(imperv_2018)
```

Now, downsample the imperviousness raster map from a 20m native resolution to lower resolutions of 40m, 80m, 100m, 200m, 400m, 800m, 1km, 2km, 4km, 8km, 10km. Then we save the resulting maps into the ~/Results directory.

```{r}
output_dir <- "Results"
if (!dir.exists(output_dir)){
  dir.create(output_dir)
  cat(sprintf("Directory '%s' created.\n", output_dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", output_dir))
}

setwd(output_dir)

output_dir <- "Imperviousness"
if (!dir.exists(output_dir)){
  dir.create(output_dir)
  cat(sprintf("Directory '%s' created.\n", output_dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", output_dir))
}

setwd(output_dir)
```
```{r}
this.dir <- "2006"
if (!dir.exists(this.dir)){
  dir.create(this.dir)
  cat(sprintf("Directory '%s' created.\n", this.dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", this.dir))
}

setwd(this.dir)

downsampled40m_2006 <- st_downsample(imperv_2006, c(1,1))
downsampled80m_2006 <- st_downsample(imperv_2006, c(3,3))
downsampled100m_2006 <- st_downsample(imperv_2006, c(4,4))
downsampled200m_2006 <- st_downsample(imperv_2006, c(9,9))
downsampled400m_2006 <- st_downsample(imperv_2006, c(19,19))
downsampled800m_2006 <- st_downsample(imperv_2006, c(39,39))
downsampled1000m_2006 <- st_downsample(imperv_2006, c(49,49))
downsampled2000m_2006 <- st_downsample(imperv_2006, c(99,99))
downsampled4000m_2006 <- st_downsample(imperv_2006, c(199,199))
downsampled8000m_2006 <- st_downsample(imperv_2006, c(399,399))
downsampled10000m_2006 <- st_downsample(imperv_2006, c(499,499))

ds_2006 <- list(downsampled40m_2006,downsampled80m_2006,downsampled100m_2006,
             downsampled200m_2006,downsampled400m_2006,downsampled800m_2006,
             downsampled1000m_2006,downsampled2000m_2006,downsampled4000m_2006,
             downsampled8000m_2006,downsampled10000m_2006)

write_stars(imperv_2006, ".tif")

for (i in seq_along(ds_2006)) {
  write_stars(ds_2006[[i]], paste0("impervious2006_downsampled_", i, ".tif"))
}
```

We repeat the same downsampling scehma from 2006, to the maps of 2009.
 
```{r}
setwd(output_dir)

this.dir <- "2009"
if (!dir.exists(this.dir)){
  dir.create(this.dir)
  cat(sprintf("Directory '%s' created.\n", this.dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", this.dir))
}

setwd(this.dir)

downsampled40m_2009 <- st_downsample(imperv_2009, c(1,1))
downsampled80m_2009 <- st_downsample(imperv_2009, c(3,3))
downsampled100m_2009 <- st_downsample(imperv_2009, c(4,4))
downsampled200m_2009 <- st_downsample(imperv_2009, c(9,9))
downsampled400m_2009 <- st_downsample(imperv_2009, c(19,19))
downsampled800m_2009 <- st_downsample(imperv_2009, c(39,39))
downsampled1000m_2009 <- st_downsample(imperv_2009, c(49,49))
downsampled2000m_2009 <- st_downsample(imperv_2009, c(99,99))
downsampled4000m_2009 <- st_downsample(imperv_2009, c(199,199))
downsampled8000m_2009 <- st_downsample(imperv_2009, c(399,399))
downsampled10000m_2009 <- st_downsample(imperv_2009, c(499,499))

ds_2009 <- list(downsampled40m_2009,downsampled80m_2009,downsampled100m_2009,
             downsampled200m_2009,downsampled400m_2009,downsampled800m_2009,
             downsampled1000m_2009,downsampled2000m_2009,downsampled4000m_2009,
             downsampled8000m_2009,downsampled10000m_2009)

write_stars(imperv_2009, "impervious2009_20m.tif")

for (i in seq_along(ds_2009)) {
  write_stars(ds_2009[[i]], paste0("impervious2009_downsampled_", i, ".tif"))
}
```

And again for 2012.

```{r}
setwd(output_dir)

this.dir <- "2012"
if (!dir.exists(this.dir)){
  dir.create(this.dir)
  cat(sprintf("Directory '%s' created.\n", this.dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", this.dir))
}

setwd(this.dir)

downsampled40m_2012 <- st_downsample(imperv_2012, c(1,1))
downsampled80m_2012 <- st_downsample(imperv_2012, c(3,3))
downsampled100m_2012 <- st_downsample(imperv_2012, c(4,4))
downsampled200m_2012 <- st_downsample(imperv_2012, c(9,9))
downsampled400m_2012 <- st_downsample(imperv_2012, c(19,19))
downsampled800m_2012 <- st_downsample(imperv_2012, c(39,39))
downsampled1000m_2012 <- st_downsample(imperv_2012, c(49,49))
downsampled2000m_2012 <- st_downsample(imperv_2012, c(99,99))
downsampled4000m_2012 <- st_downsample(imperv_2012, c(199,199))
downsampled8000m_2012 <- st_downsample(imperv_2012, c(399,399))
downsampled10000m_2012 <- st_downsample(imperv_2012, c(499,499))

ds_2012 <- list(downsampled40m_2012,downsampled80m_2012,downsampled100m_2012,
             downsampled200m_2012,downsampled400m_2012,downsampled800m_2012,
             downsampled1000m_2012,downsampled2000m_2012,downsampled4000m_2012,
             downsampled8000m_2012,downsampled10000m_2012)

write_stars(imperv_2012, "impervious2012_20m.tif")

for (i in seq_along(ds_2012)) {
  write_stars(ds_2012[[i]], paste0("impervious2012_downsampled_", i, ".tif"))
}
```

And 2015.

```{r}
setwd(output_dir)

this.dir <- "2015"
if (!dir.exists(this.dir)){
  dir.create(this.dir)
  cat(sprintf("Directory '%s' created.\n", this.dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", this.dir))
}

setwd(this.dir)

downsampled40m_2015 <- st_downsample(imperv_2015, c(1,1))
downsampled80m_2015 <- st_downsample(imperv_2015, c(3,3))
downsampled100m_2015 <- st_downsample(imperv_2015, c(4,4))
downsampled200m_2015 <- st_downsample(imperv_2015, c(9,9))
downsampled400m_2015 <- st_downsample(imperv_2015, c(19,19))
downsampled800m_2015 <- st_downsample(imperv_2015, c(39,39))
downsampled1000m_2015 <- st_downsample(imperv_2015, c(49,49))
downsampled2000m_2015 <- st_downsample(imperv_2015, c(99,99))
downsampled4000m_2015 <- st_downsample(imperv_2015, c(199,199))
downsampled8000m_2015 <- st_downsample(imperv_2015, c(399,399))
downsampled10000m_2015 <- st_downsample(imperv_2015, c(499,499))

ds_2015 <- list(downsampled40m_2015,downsampled80m_2015,downsampled100m_2015,
             downsampled200m_2015,downsampled400m_2015,downsampled800m_2015,
             downsampled1000m_2015,downsampled2000m_2015,downsampled4000m_2015,
             downsampled8000m_2015,downsampled10000m_2015)

write_stars(imperv_2015, ".tif")

for (i in seq_along(ds_2015)) {
  write_stars(ds_2015[[i]], paste0("impervious2015_downsampled_", i, ".tif"))
}
```

As for 2018, since the native resolution for this map is 10m, instead we first downsample it to the same base resolution of 20m as the previous maps in the time-series. Then we perform the same downsampling schema.

```{r}
setwd(output_dir)

this.dir <- "2018"
if (!dir.exists(this.dir)){
  dir.create(this.dir)
  cat(sprintf("Directory '%s' created.\n", this.dir))
} else {
  cat(sprintf("Directory '%s' already exists.\n", this.dir))
}

setwd(this.dir)

downsampled20m_2018 <- st_downsample(imperv_2018, c(1,1))
downsampled40m_2018 <- st_downsample(downsampled20m_2018, c(1,1))
downsampled80m_2018 <- st_downsample(downsampled20m_2018, c(3,3))
downsampled100m_2018 <- st_downsample(downsampled20m_2018, c(4,4))
downsampled200m_2018 <- st_downsample(downsampled20m_2018, c(9,9))
downsampled400m_2018 <- st_downsample(downsampled20m_2018, c(19,19))
downsampled800m_2018 <- st_downsample(downsampled20m_2018, c(39,39))
downsampled1000m_2018 <- st_downsample(downsampled20m_2018, c(49,49))
downsampled2000m_2018 <- st_downsample(downsampled20m_2018, c(99,99))
downsampled4000m_2018 <- st_downsample(downsampled20m_2018, c(199,199))
downsampled8000m_2018 <- st_downsample(downsampled20m_2018, c(399,399))
downsampled10000m_2018 <- st_downsample(downsampled20m_2018, c(499,499))

ds_2018 <- list(downsampled20m_2018,downsampled40m_2018,downsampled80m_2018,
                downsampled100m_2018,downsampled200m_2018,downsampled400m_2018,
                downsampled800m_2018,downsampled1000m_2018,downsampled2000m_2018,
                downsampled4000m_2018,downsampled8000m_2018,downsampled10000m_2018)


for (i in seq_along(ds_2018)) {
  write_stars(ds_2018[[i]], paste0("impervious2018_downsampled_", i, ".tif"))
}
```

The time-series of binary imperviousness maps from 2006 to 2018, along with their downsampled by-products are saved.

The next part of the analysis addresses the statistical standard error variances.
