---
title: "Results Figures"
author: "Yomna Eid"
date: "2026-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages and check for the correct working directory, and make sure that the data is locally present in the ./Data, and the results in the ./Results folder within your directory. 

```{r}
library(stars)
library(osmdata)
library(ggplot2)
library(dplyr)
library(extrafont)

getwd()
# or
#setwd("./Results/Imperviousness")
```

Sort the downsampled raster files into lists based on their resolution:

```{r}
imp20m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_20m.tif$", recursive = TRUE,  full.names = TRUE)
imp40m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_40m.tif$", recursive = TRUE,  full.names = TRUE)
imp80m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_80m.tif$", recursive = TRUE,  full.names = TRUE)
imp100m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_100m.tif$", recursive = TRUE,  full.names = TRUE)
imp200m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_200m.tif$", recursive = TRUE,  full.names = TRUE)
imp400m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_400m.tif$", recursive = TRUE,  full.names = TRUE)
imp800m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_800m.tif$", recursive = TRUE,  full.names = TRUE)
imp1000m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_1000m.tif$", recursive = TRUE,  full.names = TRUE)
imp2000m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_2000m.tif$", recursive = TRUE,  full.names = TRUE)
imp4000m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_4000m.tif$", recursive = TRUE,  full.names = TRUE)
imp8000m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_8000m.tif$", recursive = TRUE,  full.names = TRUE)
imp10000m_files <- list.files(path = "./Results/Imperviousness", pattern = "\\_10000m.tif$", recursive = TRUE,  full.names = TRUE)
```

Load the standard error values computed in the previous step for the time-series:

```{r}
load("./Results/Imperviousness/2006_sampling.rda")
se_mc2006 <- se_mc
se_gq2006 <- se_gq
load("./Results/Imperviousness/2009_sampling.rda")
se_mc2009 <- se_mc
se_gq2009 <- se_gq
load("./Results/Imperviousness/2012_sampling.rda")
se_mc2012 <- se_mc
se_gq2012 <- se_gq
load("./Results/Imperviousness/2015_sampling.rda")
se_mc2015 <- se_mc
se_gq2015 <- se_gq
load("./Results/Imperviousness/2018_sampling.rda")
se_mc2018 <- se_mc
se_gq2018 <- se_gq

cs <- c("20","40", "80", "100", "200", "400", "800", "1000", "2000", "4000", "8000", "10000")
```

Load and read the raster files for the 20m native resolution, then label them for each time-stamp year of the time-series:

```{r}
imperv_20m = lapply(imp20m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})
for (i in 1:length(imperv_20m)){
  imperv_20m[[i]][is.na(imperv_20m[[i]])] <- 0
}

imp_fraction_20m = lapply(imperv_20m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_20m) <- year
imp_fraction_20m
```

Repeat for the 40m resolution, and harmonize the time-stamp for year 2018 with the rest of the time-series (due to changes in the offset values). Plot to check:

```{r}
imperv_40m = lapply(imp40m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_40m[[5]] <- read_stars(imp40m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_40m[[5]])

dims$x$offset <- st_dimensions(imperv_40m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_40m[[4]])$y$offset

st_dimensions(imperv_40m[[5]]) <- dims

imperv_40m[[5]] <- st_crop(imperv_40m[[5]], p)

for (i in 1:length(imperv_40m)){
  imperv_40m[[i]][is.na(imperv_40m[[i]])] <- 0
}

# Calculate the imperviousness fraction
imp_fraction_40m = lapply(imperv_40m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_40m) <- year
imp_fraction_40m

ggplot() +
  #geom_sf(data = t, fill = NA, color = "red") +
  geom_sf(data = p, fill = "lightgreen", color = "darkgreen") +
  #geom_sf(data = imperv_40m[[5]], fill = "red", alpha = 0.5, color = "red", size = 1) +
  geom_tile(data = na.omit(as.data.frame(imperv_40m[[5]]), xy = TRUE), aes(x = x, y = y, fill = values)) +   # Raster
  geom_tile(data = na.omit(as.data.frame(imperv_40m[[4]]), xy = TRUE), aes(x = x, y = y, fill = values)) +   # Raster
  theme_minimal() +
  ggtitle("Imperviousness Polygon Overlaid on Münster - Year 2018")

```

Repeat for 80m resolution:

```{r}
imperv_80m = lapply(imp80m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_80m[[5]] <- read_stars(imp80m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_80m[[5]])

dims$x$offset <- st_dimensions(imperv_80m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_80m[[4]])$y$offset

st_dimensions(imperv_80m[[5]]) <- dims

imperv_80m[[5]] <- st_crop(imperv_80m[[5]], p)

for (i in 1:length(imperv_80m)){
  imperv_80m[[i]][is.na(imperv_80m[[i]])] <- 0
}

imp_fraction_80m = lapply(imperv_80m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_80m) <- year
imp_fraction_80m
```

Repeat for 100m resolution:

```{r}
imperv_100m = lapply(imp100m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_100m[[5]] <- read_stars(imp100m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_100m[[5]])

dims$x$offset <- st_dimensions(imperv_100m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_100m[[4]])$y$offset

st_dimensions(imperv_100m[[5]]) <- dims

imperv_100m[[5]] <- st_crop(imperv_100m[[5]], p)

for (i in 1:length(imperv_100m)){
  imperv_100m[[i]][is.na(imperv_100m[[i]])] <- 0
}

imp_fraction_100m = lapply(imperv_100m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_100m) <- year
imp_fraction_100m
```

Repeat for 200m resolution:

```{r}
imperv_200m = lapply(imp200m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_200m[[5]] <- read_stars(imp200m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_200m[[5]])

dims$x$offset <- st_dimensions(imperv_200m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_200m[[4]])$y$offset

st_dimensions(imperv_200m[[5]]) <- dims

imperv_200m[[5]] <- st_crop(imperv_200m[[5]], p)

for (i in 1:length(imperv_200m)){
  imperv_200m[[i]][is.na(imperv_200m[[i]])] <- 0
}

imp_fraction_200m = lapply(imperv_200m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_200m) <- year
imp_fraction_200m
```

Repeat for 400m resolution:

```{r}
imperv_400m = lapply(imp400m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_400m[[5]] <- read_stars(imp400m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_400m[[5]])

dims$x$offset <- st_dimensions(imperv_400m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_400m[[4]])$y$offset

st_dimensions(imperv_400m[[5]]) <- dims

imperv_400m[[5]] <- st_crop(imperv_400m[[5]], p)

for (i in 1:length(imperv_400m)){
  imperv_400m[[i]][is.na(imperv_400m[[i]])] <- 0
}

imp_fraction_400m = lapply(imperv_400m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_400m) <- year
imp_fraction_400m
```

Repeat for 800m resolution:

```{r}
imperv_800m = lapply(imp800m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_800m[[5]] <- read_stars(imp800m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_800m[[5]])

dims$x$offset <- st_dimensions(imperv_800m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_800m[[4]])$y$offset

st_dimensions(imperv_800m[[5]]) <- dims

imperv_800m[[5]] <- st_crop(imperv_800m[[5]], p)

for (i in 1:length(imperv_800m)){
  imperv_800m[[i]][is.na(imperv_800m[[i]])] <- 0
}

imp_fraction_800m = lapply(imperv_800m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_800m) <- year
imp_fraction_800m
```

Repeat for 1000m resolution:

```{r}
imperv_1000m = lapply(imp1000m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_1000m[[5]] <- read_stars(imp1000m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_1000m[[5]])

dims$x$offset <- st_dimensions(imperv_1000m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_1000m[[4]])$y$offset

st_dimensions(imperv_1000m[[5]]) <- dims

imperv_1000m[[5]] <- st_crop(imperv_1000m[[5]], p)

for (i in 1:length(imperv_1000m)){
  imperv_1000m[[i]][is.na(imperv_1000m[[i]])] <- 0
}

imp_fraction_1000m = lapply(imperv_1000m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_1000m) <- year
imp_fraction_1000m
```

Repeat for 2000m resolution:

```{r}
imperv_2000m = lapply(imp2000m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_2000m[[5]] <- read_stars(imp2000m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_2000m[[5]])

dims$x$offset <- st_dimensions(imperv_2000m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_2000m[[4]])$y$offset

st_dimensions(imperv_2000m[[5]]) <- dims

imperv_2000m[[5]] <- st_crop(imperv_2000m[[5]], p)

for (i in 1:length(imperv_2000m)){
  imperv_2000m[[i]][is.na(imperv_2000m[[i]])] <- 0
}

imp_fraction_2000m = lapply(imperv_2000m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_2000m) <- year
imp_fraction_2000m
```

Repeat for 4000m resolution:

```{r}
imperv_4000m = lapply(imp4000m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_4000m[[5]] <- read_stars(imp4000m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_4000m[[5]])

dims$x$offset <- st_dimensions(imperv_4000m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_4000m[[4]])$y$offset

st_dimensions(imperv_4000m[[5]]) <- dims

imperv_4000m[[5]] <- st_crop(imperv_4000m[[5]], p)

for (i in 1:length(imperv_4000m)){
  imperv_4000m[[i]][is.na(imperv_4000m[[i]])] <- 0
}

imp_fraction_4000m = lapply(imperv_4000m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_4000m) <- year
imp_fraction_4000m
```

Repeat for 8000m resolution:

```{r}
imperv_8000m = lapply(imp8000m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_8000m[[5]] <- read_stars(imp8000m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_8000m[[5]])

dims$x$offset <- st_dimensions(imperv_8000m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_8000m[[4]])$y$offset

st_dimensions(imperv_8000m[[5]]) <- dims

imperv_8000m[[5]] <- st_crop(imperv_8000m[[5]], p)

for (i in 1:length(imperv_8000m)){
  imperv_8000m[[i]][is.na(imperv_8000m[[i]])] <- 0
}

imp_fraction_8000m = lapply(imperv_8000m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_8000m) <- year
imp_fraction_8000m
```

Repeat for 10km resolution:

```{r}
imperv_10000m = lapply(imp10000m_files, function(file) {read_stars(file, NA_value = 250, proxy = FALSE) %>%  st_crop(p) %>% setNames("values")})

# Correct offset in 2018 causing chaos
imperv_10000m[[5]] <- read_stars(imp10000m_files[[5]], NA_value = 250, proxy = FALSE) %>% setNames("values")

dims <- st_dimensions(imperv_10000m[[5]])

dims$x$offset <- st_dimensions(imperv_10000m[[4]])$x$offset
dims$y$offset <- st_dimensions(imperv_10000m[[4]])$y$offset

st_dimensions(imperv_10000m[[5]]) <- dims

imperv_10000m[[5]] <- st_crop(imperv_1000m[[5]], p)

for (i in 1:length(imperv_10000m)){
  imperv_10000m[[i]][is.na(imperv_10000m[[i]])] <- 0
}

imp_fraction_10000m = lapply(imperv_10000m, function(object) mean(object$values))

year = c(2006, 2009, 2012, 2015, 2018)
names(imp_fraction_10000m) <- year
imp_fraction_10000m
```
  
```{r}
cs <- c("20","40", "80", "100", "200", "400", "800", "1000", "2000", "4000", "8000", "10000")

year <- c(2006, 2009, 2012, 2015, 2018)
resolutions <- cs

# Import fonts once, as the font "Rockwell" was imported seperately
# Optional step

font_import() 
loadfonts(device = "win")  # for Windows

## 1. Grey baseline (20 m) repeated

y_baseline <- as.numeric(imp_fraction_20m)
df_base <- data.frame(
  year = rep(year, times = length(resolutions)),
  value = rep(y_baseline, times = length(resolutions)),
  resolution = rep(paste0(resolutions, " m"), each = length(year))
)

## 2. Methods (MC & GQ) per resolution

df_methods <- lapply(resolutions, function(res) {
  
  y <- as.numeric(get(paste0("imp_fraction_", res, "m")))
  
  e_mc <- as.numeric(c(se_mc2006[res], se_mc2009[res], se_mc2012[res],
                       se_mc2015[res], se_mc2018[res]))
  
  e_gq <- as.numeric(c(se_gq2006[res], se_gq2009[res], se_gq2012[res],
                       se_gq2015[res], se_gq2018[res]))
  
  rbind(
    data.frame(year, value = y, error = e_mc,
               method = "Monte-Carlo", resolution = paste0(res, " m")),
    data.frame(year, value = y, error = e_gq,
               method = "Gauss-Quadrature", resolution = paste0(res, " m"))
  )
}) %>% bind_rows()

## 3. Factor for numeric ordering (alphabetical instead of numeric)

df_base$resolution <- factor(df_base$resolution, levels = paste0(resolutions, " m"))
df_methods$resolution <- factor(df_methods$resolution, levels = paste0(resolutions, " m"))

## 4. Global y-axis

y_min <- min(c(df_base$value, df_methods$value - 2*df_methods$error), na.rm = TRUE)
y_max <- max(c(df_base$value, df_methods$value + 2*df_methods$error), na.rm = TRUE)
padding <- 0.02
y_limits <- c(y_min - padding, y_max + padding)

## Optional
## 5. Professional complementary colors (muted teal & muted orange/red)

method_colors <- c("Monte-Carlo" = "#1B9E77",   
                   "Gauss-Quadrature" = "#D95F02")

## 6. Plot

p <- ggplot() +
  # Grey baseline (fixed 20 m)
  geom_line(data = df_base,
            aes(x = year, y = value),
            color = "grey50", linewidth = 0.9) +
  
  # Methods
  geom_line(data = df_methods,
            aes(x = year, y = value,
                color = method,
                linetype = method),
            linewidth = 0.8) +
  
  geom_point(data = df_methods,
             aes(x = year, y = value),
             color = method_colors[df_methods$method],
             size = 2) +  # slightly larger for visibility
  
  geom_errorbar(data = df_methods,
                aes(x = year,
                    ymin = value - 2*error,
                    ymax = value + 2*error,
                    color = method),
                width = 0.7,
                linewidth = 0.5) +
  
  facet_wrap(~ resolution, ncol = 4) +
  
  scale_color_manual(values = method_colors) +
  scale_linetype_manual(values = c("Monte-Carlo" = "dashed",
                                   "Gauss-Quadrature" = "dotted")) +
  
  labs(
    x = "Year",
    y = "Imperviousness Fraction",
    color = "Method",
    linetype = "Method"
  ) +
  
  coord_cartesian(ylim = y_limits) +  # global y-axis
  
  theme_minimal(base_size = 14) +  # larger base font
  theme(
    text = element_text(family = "Rockwell"),
    legend.position = "bottom",
    legend.title = element_blank(),
    strip.text = element_text(size = 10, face = "bold"),
    axis.text = element_text(size = 9),
    axis.title = element_text(size = 11),
    panel.grid.minor = element_blank()
  )

## 7. Save high-resolution TIFF (A4)
#  tiff("Imperviousness_facet_plot.tiff", width = 8.27, height = 11.69, units = "in",
#      res = 1200, compression = "lzw") 
# print(p)
# dev.off()

## 7. Save high-resolution PDF (A4)
cairo_pdf("Imperviousness_facet_plot.pdf", width = 8.27, height = 11.69) 
print(p)
dev.off()

# Embed the external font in the PDF
extrafont::embed_fonts("Imperviousness_facet_plot.pdf", outfile = "Imperviousness_facet_plot_embedded.pdf")
```

```{r}
save.image("Imperviousness_facet_plot.rda")
```
